sensitivity

### 2023-06-02 scripts/workshop/sensitivity.Rmd
Create sensitivity.Rmd

---
title: "dynamics"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
#define function contour(): inputs are parameters and output is values for grid search for R0
contour <- function(trans_1_min, trans_1_max, trans_3_min, trans_3_max, mort1, mort2, degr) {
  #expand data
  data <- expand_grid("trans1" = seq(from = trans_1_min, to = trans_1_max, by = 0.00001),
                      "trans2" = c(0.0001),
                      "trans3" = seq(from = trans_3_min, to = trans_3_max, by = 0.00001),
                      "shed1" = c(rep(1/2, length("trans1"))),
                      "shed2" = c(rep(1/2, length("trans1"))),
                      "reco1" = c(rep(1/10, length("trans1"))),
                      "reco2" = c(rep(1/10, length("trans1"))),
                      "mort1" = c(mort1), 
                      "mort2" = c(mort2), 
                      "degr" = c(degr), 
                      "birth1" = c(rep(5/3, length("trans1"))),
                      "birth2" = c(rep(5/3, length("trans1"))))

  #calculate disease-free equilibria for use in next-gen matrix
  data %<>% add_column(dfe1 = (data$birth1/data$mort1),dfe2 = (data$birth2/data$mort2), eigen = NA) 
  #make matrix
  mat <- matrix(1, nrow = 3, ncol = 3)

  m <- nrow(data)

  #calculate eigenvalue using next-gen matrix. max eigenvalue is R0
  for(n in 1:m){
    mat[1] = (data$trans1[n]*data$dfe1[n])/(data$reco1[n]+data$mort1[n])
    mat[2] = (data$trans1[n]*data$dfe2[n])/(data$reco2[n]+data$mort2[n])
    mat[3] = (data$shed1[n]/data$degr[n])
    mat[4] = (data$trans2[n]*data$dfe1[n])/(data$reco1[n]+data$mort1[n])
    mat[5] = (data$trans2[n]*data$dfe2[n])/(data$reco2[n]+data$mort2[n])
    mat[6] = (data$shed2[n]/data$degr[n])
    mat[7] = (data$trans3[n]*data$dfe1[n])/(data$reco1[n]+data$mort1[n])
    mat[8] = (data$trans3[n]*data$dfe2[n])/(data$reco2[n]+data$mort2[n])
    mat[9] = 0
    eigen <- max(eigen(mat)$values)
    data$eigen[n] <- eigen
  }

  data$span1 <- 1/data$mort1 #lifespan for species 1
  data$span2 <- 1/data$mort2 #lifespan for species 2
  data$half <- log(1/2)/-data$degr #viral half-life
  data$epid <- data$eigen > 1 #invasion potential (i.e. R0 > 1)
  data$prop1 <- data$trans1/data$trans2 #proportion of transmission of species 2 over species 1
  data$prop3 <- data$trans3/data$trans2 #proportion of environmental transmission over species 1
  data$prop_mort <- data$mort1/data$mort2 #relative mortality for species 1 and 2
  data$cap1 <- data$birth1/data$mort1 #carrying capacity for species 1
  data$cap2 <- data$birth2/data$mort2 #carrying capacity for species 2
  data$cap_prop <- data$cap1/data$cap2 #relative carrying capacities for species 1 and 2
  data$tot <- data$cap1 + data$cap2 #total abundance for species 1 and 2
  data$cc <- data$trans1*(data$cap1/data$tot) + data$trans2*(data$cap2/data$tot) #cc defined as transmission of a species multiplied by its relative abundance
  output <- data %>% dplyr::select(trans1, trans2, prop1, prop3, trans3, eigen, prop_mort, mort1, mort2, degr, half, cap1, cap2, cap_prop, tot, cc) %>% distinct()
  return(output)
}

reference <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = 1/45,mort2 = 1/45,degr = 1/1.947799)

composition <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = 1/60,mort2 = 1/30,degr = 1/1.947799)

size <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/52.5),mort2 = c(1/52.5),degr = 1/1.947799)

halflife <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/45),mort2 = 1/45,degr = 1/3.895598)

combined <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/70),mort2 = c(1/35),degr = 1/3.895598)
#abundance and half life
combined_1 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/45),mort2 = c(1/45),degr = 1/3.895598)
#abundance and composition
combined_2 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/70),mort2 = c(1/35),degr = 1/1.947799)
#composition and half life
combined_3 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/52.5),mort2 = c(1/52.5),degr=1/3.895598)

```

```{r}
rm0<-function(t,x,params){
  Sa <- x[1]  
  Ia <- x[2]
  Ra <- x[3]
  Sb <- x[4]  
  Ib <- x[5]
  Rb <- x[6]
  V <- x[7]
  with(as.list(params),{
    dSa <- -beta*Sa*Ia - betab*Sa*Ib - phi*Sa*V + lambda - mu_a*Sa
    dIa <- beta*Sa*Ia + betab*Sa*Ib + phi*Sa*V - alpha*Ia - mu_a*Ia
    dRa <- alpha*Ia - mu_a*Ra

    dSb <- -betab*Sb*Ib - beta*Sb*Ia - phi*Sb*V + lambda - mu_b*Sb
    dIb <- betab*Sb*Ib + beta*Sb*Ia + phi*Sb*V - alpha*Ib - mu_b*Ib
    dRb <- alpha*Ib - mu_b*Rb

    dV <- sigma*Ia + sigma*Ib - epsilon*V
    res<-c(dSa,dIa,dRa,dSb,dIb,dRb,dV)
    list(res)
  })}
#no demography
rm1<-function(t,x,params){
  Sa <- x[1]  
  Ia <- x[2]
  Ra <- x[3]
  Sb <- x[4]  
  Ib <- x[5]
  Rb <- x[6]
  V <- x[7]
  with(as.list(params),{
    dSa <- -beta*Sa*Ia - betab*Sa*Ib - phi*Sa*V
    dIa <- beta*Sa*Ia + betab*Sa*Ib + phi*Sa*V - alpha*Ia
    dRa <- alpha*Ia

    dSb <- -betab*Sb*Ib - beta*Sb*Ia - phi*Sb*V
    dIb <- betab*Sb*Ib + beta*Sb*Ia + phi*Sb*V - alpha*Ib
    dRb <- alpha*Ib

    dV <- sigma*Ia + sigma*Ib - epsilon*V
    res<-c(dSa,dIa,dRa,dSb,dIb,dRb,dV)
    list(res)
  })}

maxTime <- 300.0 # time is in years - run model for this time
times<-seq(0,maxTime,by=1) # how long we run the model for
# notes on params
# mu =     <- density-independent mortality rate
# beta =       <- contact transmission rate by infected A
# betab =       <- contact transmission rate by infected B
# phi =      <- environmental transmission rate
# lambda =       <- density-dependent growth rate
# alpha =     <- recovery rate
# sigma =    <- shedding rate
# epsilon =       <- viral degradation rate
params<-c(mu_a=1/50,
          mu_b=1/50,
          beta=0.001,
          betab=0.0001,
          phi=0.001,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/2)  # model parameters

xstart<-c(Sa=116,
          Ia=1,
          Ra=0,
          Sb=83,
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output<-as.data.frame(lsoda(xstart,times,rm0,params)) # tells computer to solve (integrate) equations

output %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ggtitle("2-Species Transmission Model for Ranavirus in an Amphibian Wetland")+theme(plot.title = element_text(hjust=0, size=10))
```

notes on params
mu =     <- density-independent mortality rate
beta =       <- contact transmission rate by infected A
betab =       <- contact transmission rate by infected B
phi =      <- environmental transmission rate
lambda =       <- density-dependent growth rate
alpha =     <- recovery rate
sigma =    <- shedding rate
epsilon =       <- viral degradation rate

transmission parameter values
species 1 is held constant at 0.0001
second species is more competent at 0.0004
env. trans rate is 0.00058

```{r}
spec_1 <- 0.0001
spec_2 <- 0.00055
env_rate <- 0.00065
param_num <- which(reference$eigen>1.103065 & reference$eigen<1.103192)
```

Neutral
```{r}
params_n <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

xstart_n <- c(Sa=params_n[[6]]/params_n[[1]],
          Ia=1,
          Ra=0,
          Sb=params_n[[6]]/params_n[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_n <- as.data.frame(lsoda(xstart_n,times,rm0,params_n)) # tells computer to solve (integrate) equations
output_n1<- as.data.frame(lsoda(xstart_n,times,rm1,params_n)) # tells computer to solve (integrate) equations

reference_eigen <- reference$eigen[param_num]
```

```{r}
output_n %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - Neutral - ", reference_eigen))+theme(plot.title = element_text(hjust=0, size=10))

output_n1 %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland w/o demo - Neutral - ", reference_eigen))+theme(plot.title = element_text(hjust=0, size=10))
```

Community Composition
```{r}
params_c <- c(mu_a=1/60,
          mu_b=1/30,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

xstart_c <- c(Sa=params_c[[6]]/params_c[[1]],
          Ia=1,
          Ra=0,
          Sb=params_c[[6]]/params_c[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_c <- as.data.frame(lsoda(xstart_c,times,rm0,params_c)) # tells computer to solve (integrate) equations
output_c1 <- as.data.frame(lsoda(xstart_c,times,rm1,params_c)) # tells computer to solve (integrate) equations

community_eigen <- composition$eigen[param_num]
```

```{r}
output_c %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - Community - ", community_eigen))+theme(plot.title = element_text(hjust=0, size=10))

output_c1 %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland w/o demo - Community - ", community_eigen))+theme(plot.title = element_text(hjust=0, size=10))
```

Abundance
```{r}
params_a <- c(mu_a=1/52.5,
          mu_b=1/52.5,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

xstart_a <- c(Sa=params_a[[6]]/params_a[[1]],
          Ia=1,
          Ra=0,
          Sb=params_a[[6]]/params_a[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_a <- as.data.frame(lsoda(xstart_a,times,rm0,params_a)) # tells computer to solve (integrate) equations
output_a1 <- as.data.frame(lsoda(xstart_a,times,rm1,params_a)) # tells computer to solve (integrate) equations

abundance_eigen <- size$eigen[param_num]
```

```{r}
output_a %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - Abundance - ", abundance_eigen))+theme(plot.title = element_text(hjust=0, size=10))

output_a1 %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland w/o demo - Abundance - ", abundance_eigen))+theme(plot.title = element_text(hjust=0, size=10))
```

Half-life
```{r}
params_h <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

xstart_h <- c(Sa=params_h[[6]]/params_h[[1]],
          Ia=1,
          Ra=0,
          Sb=params_h[[6]]/params_h[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_h <- as.data.frame(lsoda(xstart_h,times,rm0,params_h)) # tells computer to solve (integrate) equations
output_h1 <- as.data.frame(lsoda(xstart_h,times,rm1,params_h)) # tells computer to solve (integrate) equations

halflife_eigen <- halflife$eigen[param_num]
```

```{r}
output_h %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - halflife - ", halflife_eigen))+theme(plot.title = element_text(hjust=0, size=10))

output_h1 %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland w/o demo - halflife - ", halflife_eigen))+theme(plot.title = element_text(hjust=0, size=10))
```

Combined
```{r}
params_x <- c(mu_a=1/70,
          mu_b=1/35,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

#abundance and halflife
params_x1 <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

#abundance and composition
params_x2 <- c(mu_a=1/52.5,
          mu_b=1/52.5,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

#composition and halflife
params_x3 <- c(mu_a=1/60,
          mu_b=1/30,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

xstart_x <- c(Sa=params_x[[6]]/params_x[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x[[6]]/params_x[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

xstart_x1 <- c(Sa=params_x1[[6]]/params_x1[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x1[[6]]/params_x1[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

xstart_x2 <- c(Sa=params_x2[[6]]/params_x2[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x2[[6]]/params_x2[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

xstart_x3 <- c(Sa=params_x3[[6]]/params_x3[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x3[[6]]/params_x3[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_x <- as.data.frame(lsoda(xstart_x,times,rm0,params_x)) # tells computer to solve (integrate) equations
output_x1 <- as.data.frame(lsoda(xstart_x,times,rm1,params_x)) # tells computer to solve (integrate) equations
output_x2 <- as.data.frame(lsoda(xstart_x1,times,rm1,params_x1)) # tells computer to solve (integrate) equations
output_x3 <- as.data.frame(lsoda(xstart_x2,times,rm1,params_x2)) # tells computer to solve (integrate) equations
output_x4 <- as.data.frame(lsoda(xstart_x3,times,rm1,params_x3)) # tells computer to solve (integrate) equations

combined_eigen <- combined$eigen[param_num]
combined_eigen_1 <- combined_1$eigen[param_num]
combined_eigen_2 <- combined_2$eigen[param_num]
combined_eigen_3 <- combined_3$eigen[param_num]

```

```{r}
output_x %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - Combined - ", combined_eigen))+theme(plot.title = element_text(hjust=0, size=10))

output_x1 %>% ggplot(.,aes(x=time))+
  geom_line(aes(y=Sa,col="Susceptible A"))+
  geom_line(aes(y=Ia,col="Infected A"))+
  geom_line(aes(y=Ra,col="Recovered A"))+
  geom_line(aes(y=Sb,col="Susceptible B"))+
  geom_line(aes(y=Ib,col="Infected B"))+
  geom_line(aes(y=Rb,col="Recovered B"))+
  geom_line(aes(y=V,col="Virus"))+
  scale_colour_manual(values = c("red","orange","yellow","green","blue","black","violet"))+
  theme(legend.position = c(0.85,0.5))+
  labs(y="N",x="Time",col="Population")+
  ylim(0,95)+
  ggtitle(paste("2-Species Transmission Model for Ranavirus in an Amphibian Wetland - Combined - ", combined_eigen))+theme(plot.title = element_text(hjust=0, size=10))
```

Make figure with infected peaks from everything
```{r}
output_a %<>% mutate(I = Ia+Ib)
output_c %<>% mutate(I = Ia+Ib)
output_h %<>% mutate(I = Ia+Ib)
output_n %<>% mutate(I = Ia+Ib)
output_x %<>% mutate(I = Ia+Ib)

output_a1 %<>% mutate(I = Ia+Ib)
output_c1 %<>% mutate(I = Ia+Ib)
output_h1 %<>% mutate(I = Ia+Ib)
output_n1 %<>% mutate(I = Ia+Ib)
output_x1 %<>% mutate(I = Ia+Ib)
output_x2 %<>% mutate(I = Ia+Ib)
output_x3 %<>% mutate(I = Ia+Ib)
output_x4 %<>% mutate(I = Ia+Ib)

output_a1 %<>% mutate(X = I + V)
output_c1 %<>% mutate(X = I + V)
output_h1 %<>% mutate(X = I + V)
output_n1 %<>% mutate(X = I + V)
output_x1 %<>% mutate(X = I + V)
output_x2 %<>% mutate(X = I + V)
output_x3 %<>% mutate(X = I + V)
output_x4 %<>% mutate(X = I + V)
```

```{r}
color_x <- paste("Combined\nR0=", combined_eigen)
color_x2 <- paste("Abun_Half\nR0=", combined_eigen_1)
color_x3 <- paste("Abun_Comp\nR0=", combined_eigen_2)
color_x4 <- paste("Comp_Half\nR0=", combined_eigen_3)

color_c <- paste("Composition\nR0=", community_eigen)
color_a <- paste("Abundance\nR0=", abundance_eigen)
color_h <- paste("Halflife\nR0=", halflife_eigen)
color_n <- paste("Reference\nR0=", reference_eigen)

```

```{r}
ggplot()+
  geom_line(data=output_x,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c1, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a1, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h1, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=V,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c1, mapping=aes(y=V,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a1, mapping=aes(y=V,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h1, mapping=aes(y=V,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=V,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,75)+
  ggtitle(paste("Total Virions Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=X,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c1, mapping=aes(y=X,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a1, mapping=aes(y=X,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h1, mapping=aes(y=X,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=X,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,110)+
  ggtitle(paste("Total Infective Classes Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=I,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=I,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=I,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=V,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=V,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=V,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=V,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  labs(y="N",x="Time")+
  ylim(0,75)+
  ggtitle(paste("Total Virions Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```
```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=X,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=X,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=X,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=X,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=X,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,110)+
  ggtitle(paste("Total Infective Classes Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

>>>>

---
title: "sensitivity"
author: "Daniel Suh"
date: "`r Sys.Date()`"
output: html_document
---

@@
